Morphometric geometric demo: a between group analysis

### 2022-05-16 inst/gitbook/03_specific-tutorials.Rmd
sync

### Graphical options

@@

## Disparity with trees: *dispRitree!*

>>>>

### Graphical options with `...`

As mentioned above all the plots using `plot.dispRity` you can use the `...` options to add any type of graphical parameters recognised by `plot`.
However, sometimes, plotting more advanced `"dispRity"` objects also calls other generic functions such as `lines`, `points` or `legend`.
You can fine tune which specific function should be affected by `...` by using the syntax `<function>.<argument>` where `<function>` is usually the function to plot a specific element in the plot (e.g. `points`) and the `<argument>` is the specific argument you want to change for that function.
For example, in a plot containing several elements, including circles (plotted internally with `points`), you can decide to colour everything in blue using the normal `col = "blue"` option.
But you can also decide to _only_ colour the circles in blue using `points.col = "blue"`!

Here is an example with multiple elements (lines and points) taken from the [disparity with trees](#dispRitree) section below:

par(mfrow = c(2,2))
## The preview plot with the tree using only defaults
plot(time_slices, type = "preview", specific.args = list(tree = TRUE))
## The same plot but by applying general options
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     col = "blue", main = "General options")
## The same plot but by applying the colour only to the lines and change of shape only to the points
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, main = "Specific options")
## And now without the legend
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, legend = FALSE)
```

@@

## Disparity with trees: *dispRitree!* {#dispRitree}

### 2022-05-16 inst/gitbook/06_guts.Rmd
sync

####  `matrix.dispRity`

@@

```{r}
## Extracting the matrix containing the coordinates of the elements at time 50
str(matrix.dispRity(disparity, "50"))

## Extracting the 3rd bootstrapped matrix with the 2nd rarefaction level
## (15 elements) from the second group (80 Mya)
str(matrix.dispRity(disparity, subsets = 1, bootstrap = 3, rarefaction = 2))
```

@@

#### `extract.dispRity`

@@

```{r, eval=FALSE}
## Extracting the observed disparity (default)
extract.dispRity(disparity)

## Extracting the disparity from the bootstrapped values from the
## 10th rarefaction level from the second subsets (80 Mya)
extract.dispRity(disparity, observed = FALSE, subsets = 2, rarefaction = 10)
```

>>>>

####  `get.matrix`

@@

```{r}
## Extracting the matrix containing the coordinates of the elements at time 50
str(get.matrix(disparity, "50"))

## Extracting the 3rd bootstrapped matrix with the 2nd rarefaction level
## (15 elements) from the second group (80 Mya)
str(get.matrix(disparity, subsets = 1, bootstrap = 3, rarefaction = 2))
```

@@

#### `get.disparity`

@@

```{r, eval=FALSE}
## Extracting the observed disparity (default)
get.disparity(disparity)

## Extracting the disparity from the bootstrapped values from the
## 10th rarefaction level from the second subsets (80 Mya)
get.disparity(disparity, observed = FALSE, subsets = 2, rarefaction = 10)
```

### 2022-05-16 inst/gitbook/09_gmm-demo.Rmd
sync

```{r, fig.width = 8, fig.height = 16}
## Defining a the procrustes variance metric
## (as in geomorph::morphol.disparity)
proc.var <- function(matrix) {sum(matrix^2)/nrow(matrix)}
## The size metric
test_size <- test.metric(morphospace, metric = proc.var,
                         shifts = c("random", "size"))
plot(test_size)
summary(test_size)

>>>>

```{r, fig.width = 8, fig.height = 16, eval = TRUE}
## Defining a the procrustes variance metric
## (as in geomorph::morphol.disparity)
proc.var <- function(matrix) {sum(matrix^2)/nrow(matrix)}
```

```{r, fig.width = 8, fig.height = 16, eval = FALSE}

## The size metric
test_size <- test.metric(morphospace, metric = proc.var,
                         shifts = c("random", "size"))
plot(test_size)
summary(test_size)
